Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses

### 2024-12-12 manuscript_agu.tex
More improvements

\authors{Peter Kuma\affil{1,2}\thanks{}, Frida A.-M. Bender\affil{1,2}, Adrian J. McDonald\affil{3}, Simon P. Alexander\affil{4,5}, Greg M. McFarquhar\affil{6,7}, John J. Cassano\affil{8,9,10}, Graeme E. Plank\affil{3}, Sean Hartery\affil{11}, Simon Parsons\affil{12}, Sally Garrett\affil{13}, and Alex J. Schuddeboom\affil{3}}

\affiliation{1}{Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden}
\affiliation{2}{Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden}
\affiliation{3}{School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand}
\affiliation{4}{Australian Antarctic Division, Kingston, Tasmania, Australia}
\affiliation{5}{Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia}
\affiliation{6}{Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA}
\affiliation{7}{School of Meteorology, University of Oklahoma, Norman, OK, USA}
\affiliation{8}{Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA}
\affiliation{9}{National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA}
\affiliation{10}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
\affiliation{11}{Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}
\affiliation{12}{New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}
\affiliation{13}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}

@@

The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}). The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}). The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}. The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The TAN1802 data are openly available on Zenodo (\url{https://doi.org/10.5281/zenodo.4060237}). The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively. The remaining voyage data are openly available on Zenodo (\url{https://doi.org/}).

>>>>

\authors{Peter Kuma\affil{1,2,3}\thanks{}, Frida A.-M. Bender\affil{1,2}, Adrian J. McDonald\affil{3}, Simon P. Alexander\affil{4,5}, Greg M. McFarquhar\affil{6,7}, John J. Cassano\affil{8,9,10}, Graeme E. Plank\affil{3}, Sean Hartery\affil{3}\thanks{Current affiliation: Department of Physics \& Atmospheric Science, Dalhousie University, Halifax, Canada}, Simon Parsons\affil{3}\thanks{Current affiliation: New South Wales Department of Planning and Environment, Sydney, New South Wales, Australia}, Sally Garrett\affil{11}, and Alex J. Schuddeboom\affil{3}}

\affiliation{1}{Department of Meteorology (MISU), Stockholm University, Stockholm, Sweden}
\affiliation{2}{Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden}
\affiliation{3}{School of Physical and Chemical Sciences, University of Canterbury, Christchurch, Aotearoa/New Zealand}
\affiliation{4}{Australian Antarctic Division, Kingston, Tasmania, Australia}
\affiliation{5}{Australian Antarctic Program Partnership, Institute for Marine and Antarctic Studies, University of Tasmania, Hobart, Tasmania, Australia}
\affiliation{6}{Cooperative Institute of Severe and High Impact Weather Research and Operations, University of Oklahoma, Norman, OK, USA}
\affiliation{7}{School of Meteorology, University of Oklahoma, Norman, OK, USA}
\affiliation{8}{Cooperative Institute for Research in Environmental Sciences, University of Colorado, Boulder, CO, USA}
\affiliation{9}{National Snow and Ice Data Center, University of Colorado, Boulder, CO, USA}
\affiliation{10}{Department of Atmospheric and Oceanic Sciences, University of Colorado, Boulder, CO, USA}
\affiliation{11}{New Zealand Defence Force, Wellington, Aotearoa/New Zealand}

@@

The RV \emph{Polarstern} datasets are openly available on Pangaea (\url{https://pangaea.de}), as listed in Table~\ref{tab:voyage-references}. The MARCUS and MICRE datasets are openly available from ARM (\url{https://www.arm.gov}). The MERRA-2 data are openly available from the NASA Goddard Earth Sciences (GES) Data and Information Services Center (DISC) (\url{https://disc.gsfc.nasa.gov/datasets?project=MERRA-2}). The ERA5 data are openly available from the Copernicus Climate Data Store (CDS) (\url{https://cds.climate.copernicus.eu}). The ICON data are available on the Levante cluster of the DKRZ (\url{https://www.dkrz.de/en/systems/hpc/hlre-4-levante}) after registration at \url{https://luv.dkrz.de/register/}. The CERES products are openly available from the project website (\url{https://ceres.larc.nasa.gov}) and the NASA Atmospheric Science Data Centre (\url{https://asdc.larc.nasa.gov/project/CERES}). The TAN1802 data are openly available on Zenodo \cite{kremser2020}. The code for performing the presented analysis and precipitation detection is open-source and available at \url{https://github.com/peterkuma/icon-so-2024} and \url{https://github.com/peterkuma/alcf-precip}, respectively. The remaining voyage data (AA15-16, HMNZSW16, NBP1704, TAN1502, and TAN1702) are openly available on Zenodo (\url{https://doi.org/}).
